---
title: "Exploratory Data Analysis"
output: html_notebook
---


```{r}
library(tidyverse)
library(ggplot2)
library(skimr)

# library(ggplot2)
# library(tibble)
# library(dplyr)
# library(skimr)
```


```{r}
diamonds
```

```{r}
glimpse(diamonds)

```
```{r}
summary(diamonds)
```


```{r}
str(diamonds)
```

```{r}
dim(diamonds)
```
```{r}
skim(diamonds)
```

```{r}
View(diamonds)
```

# Visualizing Distributions

## Categorical Variables
```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x=cut))
```
```{r}
diamonds %>%
  count(cut)
```

```{r}
table(diamonds$cut)
```
```{r}
unique(diamonds$cut)
```
```{r}
levels(diamonds$clarity)
```
```{r}
table(diamonds$cut, diamonds$clarity)
```
```{r}
diamonds %>%
  count(cut, clarity)
```

# Plot for relationship between categorical variables
```{r}
ggplot(diamonds, aes(x=cut, fill = clarity)) +
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))
```
```{r}
ggplot(diamonds, aes(x=cut, fill = clarity)) +
  geom_bar(position = "dodge") +
  coord_flip()
```
```{r}
ggplot(diamonds, aes(x=cut, fill = clarity)) +
  geom_bar(position = "fill") +
  ylab("Proportion")
```
```{r}
prop.table(table(diamonds$cut, diamonds$clarity))
```
```{r}
round(prop.table(table(diamonds$cut, diamonds$clarity))*100, 2)
```


```{r}
ggplot(diamonds, aes(x=cut)) +
  geom_bar() +
  facet_wrap(~ clarity)
```
# Continuous Variables
```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = carat), binwidth = 0.25)
```

```{r}
diamonds %>%
  count(cut_width(carat, 0.5))
```

# Lets zoom into diamond with size less than
```{r}
smaller <- diamonds %>%
  filter(carat < 3)

ggplot(data = smaller, mapping = aes(x=carat)) +
  geom_histogram(binwidth = 0.1)
```
```{r}
ggplot(data = smaller, mapping = aes(x=carat, color=cut)) +
  geom_freqpoly(binwidth = 0.1)
```
```{r}
ggplot(data = smaller, mapping = aes(x=carat)) +
  geom_histogram(binwidth = 0.01)
```
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x=y), binwidth = 0.5) +
  coord_cartesian(ylim = c(0,50))
```
## unusual values
```{r}
diamonds %>%
  filter(y < 3 | y >20) %>%
  select(price, x, y, z) %>%
  arrange(y)
  
```

# Missing Values
```{r}

diamonds2 <- diamonds %>%
  filter(y > 3  & y <20)

ggplot(data = diamonds2)  +
  geom_histogram(mapping = aes(x=y), binwidth = 0.5)
```
# with unusual values
```{r}
ggplot(data = diamonds)  +
  geom_histogram(mapping = aes(x=y), binwidth = 0.5)

```
# Correlation between x and y with outliers
```{r}
diamonds %>%
  ggplot(aes(x=x, y=y)) +
  geom_point()
```



# Correlation between x and y with outliers relaced with NA
```{r}
diamonds %>%
  mutate(y = ifelse(y<3 | y>20, NA, y)) %>%
  ggplot(aes(x=x, y=y)) +
  geom_point()

```

# Covariation

## Categorical vs Continuous
```{r}
ggplot(data=diamonds, aes(x=price)) +
  geom_freqpoly(aes(color=cut), binwidth=500)
```

### Density Plot
```{r}
ggplot(diamonds, aes(x=price, y=..density..))+
  geom_freqpoly(aes(color=cut), binwidth=500)
```

# Box Plot
```{r}
ggplot(diamonds, aes(x=cut, y=price)) +
  geom_boxplot()

```

## Categorical vs Categorical
```{r}
ggplot(diamonds) +
  geom_count(aes(x=cut, y= color))
```

```{r}
diamonds %>%
  count(color, cut) %>%
  ggplot(aes(x=color, y=cut)) +
  geom_tile(aes(fill=n))
```
