---
title: "Linear Regression: A near Real Model with Diamonds"
output: html_notebook
---

# Building a model to predict diamond price

## loading libraries
```{r}
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(skimr)
library(corrr)
```



```{r}
diamonds
```

### Lets start working only with numberical variables

```{r}
diamonds %>%
  select(where(~ !is.factor(.x))) %>%
  corrr::correlate() %>%
  corrr::fashion()

```

### Lets build a correlation network plot
```{r}
diamonds %>%
  select(where(~ !is.factor(.x))) %>%
  corrr::correlate() %>%
  corrr::network_plot()

```

### finding the correlation b/w other variables and price
```{r}

diamonds %>%
  select(where(~ !is.factor(.x))) %>%
  corrr::correlate() %>%
  corrr::focus(price) %>%
  arrange(desc(price))
  
```

### Fetch variable names with correlation greater than 0.5
```{r}
high_corr_variables <- diamonds %>%
  select(where(~ !is.factor(.x))) %>%
  corrr::correlate() %>%
  corrr::focus(price) %>%
  arrange(desc(price)) %>%
  filter(price > 0.5) %>%
  pull(term)

high_corr_variables
```

### Lets get the data with only these variables and price
```{r}
data <- diamonds %>%
  select(high_corr_variables, price)

data
```
### split the training and testing data
```{r}
data_split <- initial_split(data, strata = price)
data_training <- training(data_split)
data_testing <- testing(data_split)
data_training

```

### building a model using lm
```{r}
model <- lm(price ~ ., data=data_training)
```

### summary of the model
```{r}
summary(model)
```

#### summary using broom
```{r}
broom::tidy(model)
```

### Consider all the variables of diamond
```{r}
complete_data <- diamonds
complete_data_split <- initial_split(complete_data, strata = price)
complete_data_training <- training(complete_data_split)
complete_data_testing <- testing(complete_data_split)
complete_model <- lm(price ~ ., data=complete_data_training)
summary(complete_model)

```

```{r}
broom::tidy(complete_model)
```

# The tidy models approach

## Split the data
```{r}
tidy_data_split <- initial_split(diamonds, strata = price)
tidy_data_train <- training(tidy_data_split)
tidy_data_test <- testing(tidy_data_split)

```

## Data Preprocessing
```{r}
data_rec <- tidy_data_train %>%
  recipe(price ~ ., tidy_data_train) %>%
  step_dummy(all_nominal()) %>%
  step_normalize(all_numeric(), -all_outcomes())%>%
  prep()

juiced <- juice(data_rec)
juiced
```

## Create a model using lm
```{r}
lm_model <- parsnip::linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")
```

## fitting the model
```{r}
lm_fit <- parsnip::fit(lm_model, price ~ ., juiced)
lm_fit
```
```{r}
glance(lm_fit)
```

```{r}
broom::tidy(lm_fit)
```

```{r}
results_train <- lm_fit %>%
  predict(new_data = juiced) %>%
  mutate(truth = tidy_data_train$price)

results_test <- lm_fit %>%
  predict(new_data = bake(data_rec, tidy_data_test)) %>%
  mutate(truth = tidy_data_test$price)

results <- results_train %>%
  mutate(type = "train") %>%
  bind_rows(
    results_test %>%
      mutate(type = "test")
  )
results
```


```{r}
results %>%
  group_by(type) %>%
  yardstick::rmse(truth, .pred)
```
# Prediction vs truth
```{r}
ggplot(results, aes(truth, .pred)) +
  geom_point() +
  geom_abline(color="red", size=2) +
  coord_fixed()

```